Deep learning on psychological arousal classification

### 2015-05-07 paper/paper.tex
Baseline classifiers! (the longest section)
data processing

The data was processed with %TODO: asdfasdfasdf how did siegle process the data??
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other

\section{Techniques} \label{section:techniques}
%TODO: we thought technology x would be a great idea because it has these advantages over the sucky way that one guy was doing it. so we wrote some code and did it. we wrote the code. :o
%-Deep learning
% -deep nets
% -dropout
% -autoencoder
% -denoising autoencoder
% -convolutional neural nets
\subsection{Convolutional Neural Networks}
Convolutional neural networks (CNNs) \cite{DBLP:conf/nips/KrizhevskySH12} are neural networks that are not fully connected: instead, each neuron has a limited field of inputs, which overlaps with the fields of adjacent neurons on its layer.  This technique has found success in image processing, as it mimics the functioning of the human brain's visual cortex.  It has also been applied to EEG analysis \cite{DBLP:journals/pami/CecottiG11}, which we attempt in two different ways.  In the first, time-based convolution, we represent our input sample as a series of time points, each of which consists of a vector of features over several channels; the convolutional neurons' fields consist of overlapping slices of time.  In the second, channel-based convolution, the sample is represented as a series of channels, each of which consists of a vector of data points from that channel over time; the convolutional neurons' fields are sets of channels.  We also use a max-pooling downsampling layer above the convolutional layer; this downsamples the results of the convolution by keeping only the maximum value out of each of a set of non-overlapping regions of the convolutional layer.  Finally, we apply a logistic regression classifier to the results of the downsampling to obtain a classification.
% -parameterized rectifiers
\subsection{Parameterized Rectifiers}
Parameterized rectified linear units (PReLUs) \cite{DBLP:journals/corr/HeZR015} are leaky ReLUs whose slopes are learnable parameters.
% -batchnorm (plus all that other stuff)
\subsection{Batch Normalization}
Batch normalization \cite{DBLP:journals/corr/IoffeS15} is a method for training deep neural networks that makes normalization a part of the network, allowing for better performance and training speed.
%-Ensemble
% -random forest
% -classifier fusion

\section{Experiment} \label{section:experiment}
%TODO: we're not making up numbers here yo.
%-Cross-validation
%-Parameter search
%-Evaluation
% -baseline classifiers
% -auc, acc, best-cutoff
\subsection{Evaluation Metrics}
\subsubsection{Accuracy}
The output of our classifiers when classifying input $x$ into category $A$ or $B$ is two probabilities $P(A_x)$ and $P(B_x)$ (the predicted probability that $x$ is in category $A$ or $B$ respectively), with $P(A_x)+P(B_x)=1$.  We choose the greater of these probabilities and declare its category to be the predicted category for $x$.  The accuracy of the classifier over a set of input samples is then simply the percentage of samples for which the predicted and actual categories agree.
\subsubsection{Best-Cutoff Accuracy}
Best-cutoff accuracy is a generalization of our accuracy calculation described above.  The only change is in how the predicted category for a sample is determined: a cutoff $c$ is set, with the sample declared to be in category $A$ if $P(A_x) > c$ and category $B$ otherwise.  Each time that the best-cutoff accuracy is computed for a set of predictions, the value of the cutoff is dynamically chosen such that the final accuracy result is maximized.
\subsubsection{AUC}
The area under the receiver operating characteristic (ROC) curve has been proposed \cite{DBLP:conf/ijcai/LingHZ03} as a more effective metric for comparing classifiers than accuracy.  The ROC curve represents the ratio of the true positive rate of a classifier to its false positive rate as its discrimination cutoff is varied.  We arbitrarily select one class here to be the positive class and the other to be the negative class.  We then construct a ranking of all input samples from least-likely to most-likely to be in the positive class (as determined by the probability assigned to that class by the classifier).  Our discrimination cutoff is then the point in this ranking list for which we determine less-likely-positive samples to be negative and more-likely ones to be positive.  We calculate the area under the ROC curve over all possible values of this cutoff, using this result as our metric.
%-Alternative evaluations
%-Ranking channels for importance

>>>>

The dataset was collected with Emotiv EPOC EEG devices. The EEG data has 14 channels at 128Hz.  The data was processed with %TODO: asdfasdfasdf how did siegle process the data??

We post-processed the resulting 128Hz signal with DFT and wavelets. We used 5 channel DFT threshholding at 0.1Hz, 4Hz, 8Hz, 12Hz, 30Hz, and 64Hz. We used Debauchey wavelets, trying a variety of wavelet decomposition depths. We also derived a number of features based on the feature set used in recent work of (citation needed) which includes eigen correlation, statistical moments, and Hjorth parameters.
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other

\section{Techniques} \label{section:techniques}
%TODO: we thought technology x would be a great idea because it has these advantages over the sucky way that one guy was doing it. so we wrote some code and did it. we wrote the code. :o
%-Deep learning
% -deep nets
% -dropout
% -autoencoder
% -denoising autoencoder
% -convolutional neural nets
% -parameterized rectifiers
Parameterized rectified linear units (PReLUs) \cite{DBLP:journals/corr/HeZR015} are leaky ReLUs whose slopes are learnable parameters.
% -batchnorm (plus all that other stuff)
Batch normalization \cite{DBLP:journals/corr/IoffeS15} is a method for training deep neural networks that makes normalization a part of the network, allowing for better performance and training speed.
%-Ensemble
% -random forest
% -classifier fusion

\section{Experiment} \label{section:experiment}
%TODO: we're not making up numbers here yo.
%-Cross-validation
%-Parameter search
%-Evaluation
% -baseline classifiers
% -auc, acc, best-cutoff
%-Alternative evaluations
%-Ranking channels for importance
